---
title: "Word Penis Data… Again"
author: "Tobi & Lukas"
date: "Rendered `r format(Sys.time(), '%F %H:%M')`"
output:
  html_document:
    toc: true
    toc_float: true
    highlight: tango
    fig_width: 9
    fig_height: 6
    theme: yeti
    code_folding: show
    lib_dir: "assets"
    self_contained: no
    include:
      after_body: _footer.html
---

```{r setup, include=F}
source("setup.R")
theme_set(theme_readthedown())
```

A while ago, [I analyzed the World Penis Data](https://blog.jemu.name/post/2015/08/i-analyzed-some-world-penis-data---because-why-not/), because let's face it, the inclined data enthusiast can't resist a dataset like [this](www.everyoneweb.com/worldpenissize). Sadly, my old code to scrape the table on that page doesn't work anymore, and I have not figured out a new way to get the data, so I have to rely on the data I saved the last time and included in the [tadaadata/loldata](github.com/tadaadata/loldata) package.  

Anyway, long story short: I don't like the look of my old analysis, because that was done in a time before I bothered with ggplot2-prettification. So now we try this again.

## Length 

### By State

```{r length_state}
penis %>% 
  gather(key = state, value = length, length_flaccid, length_erect) %>%
  mutate(state = factor(state, 
                        levels = c("length_flaccid", "length_erect"), 
                        labels =  c("Flaccid", "Erect"))) %>%
  {
    ggplot(., aes(x = length, fill = state, color = state)) +
    geom_histogram(binwidth = 1, alpha = .7, position = "dodge") +
    scale_x_continuous(breaks = seq(0, 100, 2), minor_breaks = seq(0, 100, .5)) +
    labs(title = "World Penis Data", subtitle = "Length by State",
         x = "Length (cm)", y = "Frequency", fill = "State", color = "State") +
    theme(legend.position = "top")
  }
```

### By State and Region

```{r length_state_region}
penis %>% 
  gather(key = state, value = length, length_flaccid, length_erect) %>%
  mutate(state = factor(state, 
                        levels = c("length_flaccid", "length_erect"), 
                        labels =  c("Flaccid", "Erect"))) %>%
  group_by(Region) %>%
  mutate(order_length = mean(length)) %>%
  {
    ggplot(., aes(x = reorder(Region, order_length), y = length, fill = state, color = state)) +
    geom_boxplot(alpha = .7) +
    coord_flip() +
    scale_y_continuous(breaks = seq(0, 100, 2), minor_breaks = seq(0, 100, .5)) +
    labs(title = "World Penis Data", subtitle = "Length by State",
         x = "Region", y = "Length (cm)", fill = "State", color = "State") +
    theme(axis.text.y = element_text(size = rel(1.2)),
          legend.position = "top")
  }
```

## Volume

### By State
 
```{r volume_state}
penis %>% 
  gather(key = state, value = volume, volume_flaccid, volume_erect) %>%
  mutate(state = factor(state, 
                        levels = c("volume_flaccid", "volume_erect"), 
                        labels =  c("Flaccid", "Erect"))) %>%
  {
    ggplot(., aes(x = volume, fill = state, color = state)) +
    geom_histogram(binwidth = 5, alpha = .7, position = "dodge") +
    scale_x_continuous(breaks = seq(0, 500, 25), minor_breaks = seq(0, 500, 5)) +
    labs(title = "World Penis Data", subtitle = "Volume by State",
         x = expression(paste("Volume ", (cm^3))), y = "Frequency", fill = "State", color = "State") +
    theme(legend.position = "top")
  }
```

### By State and Region

```{r volume_state_region}
penis %>% 
  gather(key = state, value = volume, volume_flaccid, volume_erect) %>%
  mutate(state = factor(state, 
                        levels = c("volume_flaccid", "volume_erect"), 
                        labels =  c("Flaccid", "Erect"))) %>%
  group_by(Region) %>%
  mutate(order_volume = mean(volume)) %>%
  {
    ggplot(., aes(x = reorder(Region, order_volume), y = volume, fill = state, color = state)) +
    geom_boxplot(alpha = .7) +
    coord_flip() +
    scale_y_continuous(breaks = seq(0, 500, 25), minor_breaks = seq(0, 500, 5)) +
    labs(title = "World Penis Data", subtitle = "Volume by State",
         x = "Region", y = expression(paste("Volume ", (cm^3))), fill = "State", color = "State") +
    theme(axis.text.y = element_text(size = rel(1.5)),
          legend.position = "top")
  }
```
