---
title: "Length"
author: "Tobi & Lukas"
date: "Rendered `r format(Sys.time(), '%F %H:%M')`"
output:
  html_document
---

```{r setup_length, include=FALSE}
source("setup.R")
```

It seems fairly pointless to plot the length of both flaccid and erect states combined, but for completion's sake, let's just get it over with.

```{r length}
penis %>% 
  gather(key = state, value = length, length_flaccid, length_erect) %>%
  mutate(state = factor(state, 
                        levels = c("length_flaccid", "length_erect"), 
                        labels =  c("Flaccid", "Erect"))) %>%
  {
    ggplot(., aes(x = length)) +
    geom_histogram(binwidth = .5, alpha = .7, position = "dodge") +
    scale_x_continuous(breaks = seq(0, 100, 2), 
                       minor_breaks = seq(0, 100, .5),
                       labels = label_cm,
                       sec.axis = sec_axis(trans = ~./2.54, 
                                           labels = label_in)) +
    labs(title = "World Penis Data", subtitle = "Length",
         x = "Length", y = "Frequency", 
         fill = "State", color = "State",
         caption = plot_caption) +
    theme(legend.position = "top")
  }
```


## By State

```{r length_state}
penis %>% 
  gather(key = state, value = length, length_flaccid, length_erect) %>%
  mutate(state = factor(state, 
                        levels = c("length_flaccid", "length_erect"), 
                        labels =  c("Flaccid", "Erect"))) %>%
  {
    ggplot(., aes(x = length, fill = state, color = state)) +
    geom_histogram(binwidth = .5, alpha = .7, position = "dodge") +
    scale_x_continuous(breaks = seq(0, 100, 2), 
                       minor_breaks = seq(0, 100, .5),
                       labels = label_cm,
                       sec.axis = sec_axis(trans = ~./2.54, 
                                           labels = label_in)) +
    scale_fill_brewer(palette = "Paired") +
    scale_color_brewer(palette = "Paired") +
    labs(title = "World Penis Data", subtitle = "Length by State",
         x = "Length", y = "Frequency", 
         fill = "State", color = "State",
         caption = plot_caption) +
    theme(legend.position = "top")
  }
```

### By State and Region

```{r length_state_region}
penis %>% 
  gather(key = state, value = length, length_flaccid, length_erect) %>%
  mutate(state = factor(state, 
                        levels = c("length_flaccid", "length_erect"), 
                        labels =  c("Flaccid", "Erect"))) %>%
  group_by(Region) %>%
  mutate(order_length = mean(length)) %>%
  {
    ggplot(., aes(x = reorder(Region, order_length), y = length, 
                  fill = state, color = state)) +
    geom_boxplot(alpha = .7) +
    coord_flip() +
    scale_y_continuous(breaks = seq(0, 100, 2), 
                       minor_breaks = seq(0, 100, .5),
                       labels = label_cm,
                       sec.axis = sec_axis(trans = ~./2.54, 
                                           labels = label_in)) +
    scale_fill_brewer(palette = "Paired") +
    scale_color_brewer(palette = "Paired") +
    labs(title = "World Penis Data", subtitle = "Length by State",
         x = "", y = "Length", fill = "State", color = "State",
         caption = plot_caption) +
    theme(axis.text.y = element_text(size = rel(1.2)),
          legend.position = "top")
  }

# CIs
penis_long %>%
  group_by(Region) %>%
  mutate(order_length = mean(length)) %>%
  {
    ggplot(data = ., aes(x = reorder(Region, order_length), y = length, color = state)) +
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar") +
    stat_summary(fun.y = mean, geom = "point", size = 2) +
    coord_flip() +
    scale_y_continuous(breaks = seq(0, 100, 2), 
                       minor_breaks = seq(0, 100, .5),
                       labels = label_cm,
                       sec.axis = sec_axis(trans = ~./2.54, 
                                           labels = label_in)) +
    scale_color_brewer(palette = "Paired") +
    labs(title = "World Penis Data", subtitle = "Length by State (mean with 95% CI)",
         x = "", y = "Length", fill = "State", color = "State",
         caption = plot_caption) +
    theme(axis.text.y = element_text(size = rel(1.2)),
          legend.position = "top")
  }
```

## Growth Factor

I calculated the length-wise growth factor based on $\frac{\text{erect length}}{\text{flaccid length}}$, which reduces the relationship of erect and flaccid length into a single variable.  
Let's look what that's all about.

```{r length_growth}
ggplot(data = penis, aes(x = growth_length)) +
  geom_histogram(binwidth = .05, alpha = .7) +
  labs(title = "World Penis Data", subtitle = "Length-wise growth factor",
         x = "Growth Factor", y = "Frequency",
         caption = plot_caption)
```

Well that seems like it justifies further investigation.

### By Region

```{r growth_length_regions}
ggplot(data = penis, aes(x = reorder(Region, growth_length), y = growth_length)) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar") +
  stat_summary(fun.y = mean, geom = "point", size = 2) +
  coord_flip() +
  scale_y_continuous(breaks = seq(0, 2, .05)) +
  labs(title = "World Penis Data", 
       subtitle = "Length-wise growth factor by region (mean with 95% CI)",
       x = "", y = "Growth Factor",
       caption = plot_caption)
```


## Erect vs. Flaccid

Seems fairly self-explanatory to suspect a relationship there, so let's see.

```{r corr_length_states}
ggplot(data = penis, aes(x = length_flaccid, y = length_erect)) +
  geom_smooth(method = lm, se = F, color = "gray") +
  geom_point(size = 2) +
  scale_x_continuous(labels = label_cm,
                     sec.axis = sec_axis(trans = ~./2.54, 
                                           labels = label_in)) +
  scale_y_continuous(labels = label_cm,
                     sec.axis = sec_axis(trans = ~./2.54, 
                                           labels = label_in)) +
  labs(title = "World Penis Data",
       subtitle = "Flaccid by Erect Length",
       x = "Flaccid Length", y = "Erect Length",
       caption = plot_caption)
```


Well that looks like a pretty decent linear relationship with some other effect we haven't identified yet.  
Since there's only so much data in this dataset, the only thing we can really do is to look at the effect of different regions.

### Averaged by Region

```{r corr_length_states_regions_mean}
penis %>% 
  group_by(Region) %>%
  summarize(length_flaccid = mean(length_flaccid),
            length_erect   = mean(length_erect)) %>%
  ggplot(data = ., aes(x = length_flaccid, y = length_erect, color = Region)) +
  geom_smooth(method = lm, se = F, color = "gray") +
  geom_point(size = 3, color = "black") +
  geom_point(size = 2) +
  scale_x_continuous(labels = label_cm,
                     sec.axis = sec_axis(trans = ~./2.54, 
                                           labels = label_in)) +
  scale_y_continuous(labels = label_cm,
                     sec.axis = sec_axis(trans = ~./2.54, 
                                           labels = label_in)) +
  scale_color_brewer(palette = "Paired") +
  labs(title = "World Penis Data",
       subtitle = "Flaccid by Erect Length (averaged by region)",
       x = "Flaccid Length", y = "Erect Length",
       caption = plot_caption)
```

That seems… reasonably informative. Let's to that again without the averaging though.

### by Region

```{r corr_length_states_regions}
ggplot(data = penis, aes(x = length_flaccid, y = length_erect, color = Region)) +
  geom_smooth(method = lm, se = F, color = "gray") +
  geom_point(size = 3, color = "black") +
  geom_point(size = 2) +
  scale_x_continuous(labels = label_cm,
                     sec.axis = sec_axis(trans = ~./2.54, 
                                           labels = label_in)) +
  scale_y_continuous(labels = label_cm,
                     sec.axis = sec_axis(trans = ~./2.54, 
                                           labels = label_in)) +
  scale_color_brewer(palette = "Paired") +
  labs(title = "World Penis Data",
       subtitle = "Flaccid by Erect Length",
       x = "Flaccid Length", y = "Erect Length",
       caption = plot_caption)
```


### Correlation

Well, we've seen enough of that I guess.  
Let's do some math:

```{r corr_length_states_lm}
model <- lm(length_erect ~ length_flaccid, data = penis)

knitr::kable(tidy(model))

knitr::kable(glance(model))
```


So… yeah. There's a perfectly valid linear relationship with a nice big $R^2$ and it basically tells us that the expected size of an erect penis will be roughly 1.4 times the size of the flaccid penis.  
Seems… realistic, I guess?

Lastly, here's a version of the above plot for you to get your hands on:

```{r corr_length_states_plotly}
text <- ~paste0("<b>", Region, "</b>",
               "<br /><b>Country:</b> ", Country,
               "<br /><b>N</b> = ", N,
               "<br /><b>Source:</b> ", Source)

plot_ly(data = penis, x = ~length_flaccid, y = ~length_erect, colors = "Paired",
        width = 768) %>%
  add_markers(color = I("black"), size = I(12), hoverinfo = "none") %>%
  add_markers(color = ~Region, hoverinfo = "text", size = I(10),
              text = text) %>%
  layout(title = "World Penis Data:<br />Erect by Flaccid Length",
         xaxis = list(title = "Flaccid Length (cm)"), 
         yaxis = list(title = "Erect Length (cm)"),
         paper_bgcolor = "#ffffff", plot_bgcolor = "#ffffff", hovermode = "closest",
         showlegend = F,
         autosize = T)
```
